---
title: "Developing Data Products Course Project 2"
author: "Jeffrey M. Hunter"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: ioslides_presentation
---

```{r setup, include = FALSE}
# set working directory
setwd("~/repos/coursera/github-assignments/developing-data-products-course-project-2")

# set knitr options
knitr::opts_chunk$set(echo = TRUE, fig.path = 'figures/')

# clear the global workspace (including hidden objects)
rm(list = ls(all.names = TRUE))

# free up memory and display statistics on free memory
gc()
```

## Synopsis

This project was created for the Developing Data Products course as part of the
Data Science Specialization offered through Coursera from Johns Hopkins
University.

The source code for this project can be found on
GitHub: <a target="_blank" href="https://github.com/oraclejavanet/developing-data-products-course-project-2">Developing Data Products Course Project 2</a>

## Objectives

The goal of the project is to create a web page presentation using R Markdown
that features a plot created with Plotly, and to host the resulting web page on
either GitHub Pages, RPubs, or NeoCities.

## Sepal Length Boxplot

```{r sepal-length-boxplot, message = FALSE, echo = FALSE}
library(plotly)

# Loading iris dataset
data(iris)
attach(iris)

#plotting a Boxplot with Sepal.Length variable and storing it in box_plot
box_plot <- plot_ly(y = Sepal.Length,
                    type = 'box',
                    color = Species)

#defining labels and title using layout()
layout(box_plot,
       title = "Iris Dataset",
       yaxis = list(title = "Sepal.Length"))
```

